---
title: "Data Quality for `r params$country` --- Countdown Analysis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  officedown::rdocx_document:
    reference_docx: report-template.docx
    page_size:
      width: !expr 11906 / 1440
      height: !expr 16838 / 1440
      orient: "portrait"
    page_margins:
      bottom: 1
      top: 1
      right: !expr 1417 / 1440
      left: !expr 1417 / 1440
      header: !expr 708 / 1440
      footer: !expr 708 / 1440
      gutter: 0
params:
  cache: NULL
  i18n: NULL

  country: NULL
  adminlevel_1: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  # fig.width = 7,
  # fig.height = 5,
  dpi = 300
)

library(cd2030.core)
library(dplyr)
library(purrr)
library(stringr)
library(reactable)
library(officedown)
library(officer)

cache <- params$cache
i18n <- params$i18n
adminlevel_1 <- params$adminlevel_1

data <- cache$countdown_data
data_years <- cache$data_years
```

## 1. Health Facility Data Quality Assessment {-}

### Background

Routinely reported health facility data are an important data source for health
indicators. The data are reported by health facilities on events such as immunizations
given, or live births attended. As with any data, quality is an issue. Data are checked
to consider completeness of reporting by health facilities, identify extreme outliers,
and internal consistency.

### Data Quality Summary Table

```{r}
translated_labels <- list(
  header = list(
    h1 = i18n$t("title_score_monthly_complete"),
    h2 = i18n$t("title_score_extreme_outliers"),
    h3 = i18n$t("title_score_consist_annual")
  ),
  section = list(
    r1a   = i18n$t("lbl_score_1a"),
            # Combine text + threshold number
    r1b   = paste0(i18n$t("lbl_score_1b_prefix"), cache$performance_threshold),
    r1c   = if (get_selected_group() == "vaccine") i18n$t("lbl_score_1c_vaccine") else i18n$t("lbl_score_1c_rmncah"),
    r2a   = i18n$t("lbl_score_2a"),
    r2b   = i18n$t("lbl_score_2b"),
    score = i18n$t("lbl_score_annual_score")
  ),
  metric = list(
    r_anc1_penta1    = i18n$t("lbl_consist_ratio_anc1_penta1"),
    r_penta1_penta3  = i18n$t("lbl_consist_ratio_penta1_penta3"),
    ok_anc1_penta1   = i18n$t("lbl_score_range_anc1_penta1"),
    ok_penta1_penta3 = i18n$t("lbl_score_range_penta1_penta3")
  )
)

overall_score <- if (is.null(adminlevel_1)) {
  cache$calculate_overall_score("national", labels = translated_labels)
} else {
  cache$calculate_overall_score("adminlevel_1", region = adminlevel_1, labels = translated_labels)
}

overall_score %>% 
  plot(data_years, width = 8, title = i18n$t("lbl_score_metric_header"))
```

### District Reporting Rates

```{r district-reporting-rates}
reporting_rate <- cache$performance_threshold
plot(cache$calculate_district_reporting_rate(
  region = adminlevel_1),
  title = str_glue(i18n$t("plt_title_rr_national")),
  caption = str_glue(i18n$t("plt_caption_rr_national")),
  indicator_labels = c(
    anc = i18n$t("opt_anc"),
    idelv = i18n$t("opt_idelv"),
    vacc = i18n$t("opt_vacc"),
    opd = i18n$t("opt_opd")
  )) +
  cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

Make a statement about the data quality overall score and trend: is it good, is it going in the right direction?

Interpret the completeness of reporting data: is it good, going in the right direction?

Interpret the data on extreme outliers: is it good, are districts doing well?

Interpret the consistency of the reported data for ANC1 and penta1 at the national level; same for penta1 and penta3.

Interpret the data on the percent of districts that have ANC1 to penta1 ratios within the expected range; same for penta1 to penta3.

---

:::


### ANC1/Penta1 and Penta1/Penta3 Ratios

```{r}
plot(
  cache$ratios_summary,
  title = i18n$t("plt_title_consist_ratios"),
  x_labels = c(
    "anc1_penta1"   = i18n$t("lbl_consist_ratio_anc1_penta1"),
    "penta1_penta3" = i18n$t("lbl_consist_ratio_penta1_penta3")
  )) +
  cd_report_theme()
```

```{r}
legend <- c(
  district = i18n$t("lbl_leg_consist_district"),
  linear_fit = i18n$t("lbl_leg_consist_linear_fit"),
  diagonale = i18n$t("lbl_leg_consist_diagonal")
)

vacc1 <- i18n$t("opt_anc1")
vacc2 <- i18n$t("opt_penta1")
plot_comparison_anc1_penta1(
  data,
  title = str_glue(i18n$t("plt_title_consist_checks")),
  x_label = vacc1,
  y_label = vacc2,
  legend = legend) +
  cd_report_theme()
```

```{r}
vacc1 <- i18n$t("opt_penta1")
vacc2 <- i18n$t("opt_penta3")
plot_comparison_penta1_penta3(
  data,
  title = str_glue(i18n$t("plt_title_consist_checks")),
  x_label = vacc1,
  y_label = vacc2,
  legend = legend)+
  cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

Interpret the consistency of the reported data for ANC1 and penta1 at the national level; same for penta1 and penta3.

Interpret the data on the percent of districts that have ANC1 to penta1 ratios within the expected range; same for penta1 to penta3.

---

:::
