---
title: "Curative Health Services for `r params$country` --- Countdown Analysis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  officedown::rdocx_document:
    reference_docx: report-template.docx
  pdf_document:
    toc: false
    latex_engine: lualatex
params:
  cache: NULL
  i18n: NULL

  country: NULL
  adminlevel_1: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  fig.width=7, 
  fig.height=5, 
  dpi=1200
)

library(cd2030.core)
library(dplyr)
library(purrr)
library(reactable)
library(officedown)
library(officer)

cache <- params$cache
i18n <- params$i18n
first_year <- min(cache$data_years)
last_year <- max(cache$data_years)
```

## Curative health services: admission and case fatality rates among children under-5

### Background

Data on inpatient admissions among under-fives are indicators of access to curative services. In-patient mortality (case fatality rates) is an indicator of quality of care. 

### Service Utilization DQA

```{r}
translated_labels <- list(
  header = list(
    h1 = i18n$t("title_score_monthly_complete"),
    h2 = i18n$t("title_score_extreme_outliers"),
    h3 = i18n$t("title_score_service_dqa") # Ensure you have a translation key for this
  ),
  indicator = list(
    opd_rr                   = i18n$t("lbl_opd_rr"), 
    district_opd_rr          = paste0(i18n$t("lbl_score_1b_prefix"), cache$performance_threshold),
    mis_opd_under5           = i18n$t("lbl_mis_opd_under5"),
    mis_ipd_under5           = i18n$t("lbl_mis_ipd_under5"),
    districts_no_missing_opd = i18n$t("lbl_districts_no_missing_opd"),
    districts_no_missing_ipd = i18n$t("lbl_districts_no_missing_ipd"),
    
    opd_under5_outlier5std   = i18n$t("lbl_opd_under5_outlier5std"),
    district_no_outlier_opd  = i18n$t("lbl_district_no_outlier_opd"),
    
    ratio_opd_u5_ipd_u5      = i18n$t("lbl_ratio_opd_u5_ipd_u5"),
    perc_opd_under5          = i18n$t("lbl_perc_opd_under5"),
    perc_ipd_under5          = i18n$t("lbl_perc_ipd_under5")
  )
)
cache$calculate_service_dqa_summary("national", labels = translated_labels) %>%
  plot(years = cache$data_years, title = i18n$t("lbl_score_metric_header"))
```

```{r, fig.cap='Figure 6a: OPD service use by children and all ages, national'}
cache$filter_service_utilization('national', 'opd') %>% 
  plot() + cd_report_theme()
```

```{r, fig.cap='Figure 6b : map with OPD service use by children, by region'}
cache$prepare_mapping_service_utlization('opd', c(first_year, last_year)) %>% 
  plot() + cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

What can be said about the data quality for OPD visits? Is there consistency of reported numbers between years? What is the % of OPD visits that are under-5 and are they within an expected range of 15-40%?? 

What is the number of OPD visits per child per year during 2019-2023, is it increasing?  Is it lower than 1 visit per year, which is considered indicative of low access? What % of OPD visits are for children under 5? 

What can be said about the OPD visits per child per year by region/province in 2023? How large is the difference between top and bottom regions? 

---

:::

## Curative health services: admission and case fatality rates among children under-5

### Background

Data on inpatient admissions among under-fives are indicators of access to curative services. In-patient mortality (case fatality rates) is an indicator of quality of care. 

```{r, fig.cap='Figure 6c: Admissions per 100 children and case fatality rates per 100 admissions under-5, national'}
cache$filter_service_utilization('national', 'ipd') %>% 
  plot() + cd_report_theme()
```

```{r, fig.cap='Figure 6b : map with OPD service use by children, by region'}
cache$prepare_mapping_service_utlization('ipd', c(first_year, last_year)) %>% 
  plot() + cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

What can be said about the data quality? Is there consistency of reported numbers of admissions / admission rates over time? Is the percent of admissions that are children under-5 plausible (within an expected range 15-40%) 

What is the number of admission per 100 children under 5 per year during 2019-2024?  Trend? Is it low or high?
What is the case fatality rate among admissions under-5, what is the trend? What does this say about the quality of care?

What can be said about admissions per 100 children under-5 per year by region/province in 2024?

---

:::


### MCH Preventive vs Curative Index

```{r}
cache$generate_admin1_mch_curative_index() %>% 
  plot(
    labels = list(
      title          = i18n$t("lbl_mch_curative_title"),
      x_axis         = i18n$t("lbl_mch_prev_index_x"),
      y_axis         = i18n$t("lbl_curative_index_y"),
      q_top_left     = i18n$t("lbl_quad_low_prev_high_cur"),
      q_top_right    = i18n$t("lbl_quad_high_prev_high_cur"),
      q_bottom_left  = i18n$t("lbl_quad_low_prev_low_cur"),
      q_bottom_right = i18n$t("lbl_quad_high_prev_low_cur")
    )
  ) + cd_report_theme()
```