---
title: "`r params$country`"
output: 
  officedown::rdocx_document:
    reference_docx: synthesis-template.docx
params:
  cache: NULL
  i18n: NULL
  adminlevel_1: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  # fig.width=7, 
  # fig.height=5, 
  dpi = 300
)

library(cd2030.core)
library(dplyr)
library(purrr)
library(reactable)
library(officedown)
library(officer)

cache <- params$cache
i18n <- params$i18n
data <- cache$countdown_data
country <- cache$country
data_years <- cache$data_years
years_range <- paste0(min(data_years, na.rm = TRUE), '-', max(data_years, na.rm = TRUE))
first_year <- min(cache$data_years)
last_year <- max(cache$data_years)

layout <- cd_multicol_factory(width = 13.93, height = 22.0, orient = "portrait", margins = c(0.5, 0.5, 0.5, 0.5))

my_multicol_start <- layout$start
my_multicol_stop <- layout$stop
```

### Analysis of reproductive, maternal, newborn, child and adolescent health indicators for `r years_range`: Synthesis chartbook 
### Countdown to 2030 in partnership with `r country`` Ministry of Health, Global Financing Facility, WHO, WAHO, UNICEF

> Country analytical team names and affiliation

# KEY FINDINGS

## 1. Health facility data quality assessment: numerators and denominators

**NUMERATORS:** Routinely reported health facility data are an important data source for health indicators. The data are reported by health facilities on events such as immunizations given, or live births attended. As with any data, quality is an issue. Data are assessed for completeness of reporting by health facilities, extreme outliers and internal consistency. Appropriate adjustments are made to the data before use to compute statistics.

#### Summary of reported health facility data quality, DHIS2, `r years_range`

`r my_multicol_start()`

```{r, fig.width=8}
translated_labels <- list(
  header = list(
    h1 = i18n$t("title_score_monthly_complete"),
    h2 = i18n$t("title_score_extreme_outliers"),
    h3 = i18n$t("title_score_consist_annual")
  ),
  section = list(
    r1a   = i18n$t("lbl_score_1a"),
            # Combine text + threshold number
    r1b   = paste0(i18n$t("lbl_score_1b_prefix"), cache$performance_threshold),
    r1c   = if (get_selected_group() == "vaccine") i18n$t("lbl_score_1c_vaccine") else i18n$t("lbl_score_1c_rmncah"),
    r2a   = i18n$t("lbl_score_2a"),
    r2b   = i18n$t("lbl_score_2b"),
    score = i18n$t("lbl_score_annual_score")
  ),
  metric = list(
    r_anc1_penta1    = i18n$t("lbl_consist_ratio_anc1_penta1"),
    r_penta1_penta3  = i18n$t("lbl_consist_ratio_penta1_penta3"),
    ok_anc1_penta1   = i18n$t("lbl_score_range_anc1_penta1"),
    ok_penta1_penta3 = i18n$t("lbl_score_range_penta1_penta3")
  )
)

overall_score <- if (is.null(adminlevel_1)) {
  cache$calculate_overall_score("national", labels = translated_labels)
} else {
  cache$calculate_overall_score("adminlevel_1", region = adminlevel_1, labels = translated_labels)
}

overall_score %>% 
  plot(data_years, width = 8, title = i18n$t("lbl_score_metric_header"))
```

`r run_columnbreak()`

::: {custom-style="Style1"}

**Interpretations**

- What is the overall quality of the data as assessed by the overall annual data quality score?
- Is there a data quality pattern by year for which there is an explanation? 
- Are there certain regions or other subnational units that are particularly problematic?
- Are there certain reporting forms or services (e.g., antenatal care, labour and delivery, immunization) that are problematic? Was an adjustment done for incomplete reporting (provide the k value)?
- Is there good consistency between reported numbers of ANC1 and penta1? If not, what could be the explanation?

:::

`r my_multicol_stop(widths = c(8, 4), space = 0.2, sep = TRUE)`

`r my_multicol_start()`

Numerator: facility data quality  - example 1
Explain the observation on data quality (one bullet)

```{r, fig.width=6.3, fig.height=3.5}
legend <- c(
  district = i18n$t("lbl_leg_consist_district"),
  linear_fit = i18n$t("lbl_leg_consist_linear_fit"),
  diagonale = i18n$t("lbl_leg_consist_diagonal")
)

vacc1 <- i18n$t("opt_anc1")
vacc2 <- i18n$t("opt_penta1")
plot_comparison_anc1_penta1(
  data,
  title = str_glue(i18n$t("plt_title_consist_checks")),
  x_label = vacc1,
  y_label = vacc2,
  legend = legend) +
  cd_report_theme()

run_columnbreak()
```
Numerator: facility data quality  - example 2
Explain the observation on data quality (one bullet)

```{r , fig.width=6.3, fig.height=3.5}
reporting_rate <- cache$performance_threshold
plot(cache$calculate_district_reporting_rate(region = adminlevel_1),
  title = str_glue(i18n$t("plt_title_rr_national")),
  caption = str_glue(i18n$t("plt_caption_rr_national")),
  indicator_labels = c(
    anc = i18n$t("opt_anc"),
    idelv = i18n$t("opt_idelv"),
    vacc = i18n$t("opt_vacc"),
    opd = i18n$t("opt_opd")
  )) +
  cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

**DENOMINATORS:** Service coverage is defined as the population who received the service (numerator) divided by the population who need the services: (the denominator). We test four options for denominator measures using institutional live births and Pent-3 immunization coverage (Figures 2c and 2d). The quality of the population projections in DHIS2 is assessed through consistency over time and comparison with the UN projections. Two denominators are also derived using near universal service such as ANC-1 and Penta-1. The most plausible is identified for use to generate other statistics.

`r my_multicol_start()`

**Total Livebirths**
```{r, fig.width=4.2}
selected_population <- cache$derivation_population
metric <- case_when(
  str_detect(selected_population, 'birth') ~ 'births',
  str_detect(selected_population, 'pop') ~ 'population',
  str_detect(selected_population, 'under1') ~ 'under1',
)

cache$denominator_metrics %>%
  plot(
    metric = metric, 
    title = i18n$t(paste0("plt_title_denom_", metric)),
    x_label = i18n$t("title_global_year"),
    y_label = i18n$t(paste0("opt_", metric)),
    legend_labels = c(i18n$t(paste0("lbl_leg_denom_un_", metric)), i18n$t(paste0("lbl_leg_denom_dhis2_", metric)))) +
  cd_report_theme()
```

**National Institutional Live Births**
```{r, fig.width=4.2}
indicator <- i18n$t("opt_instlivebirths")
cache$calculate_derived_coverage('instlivebirths', 'national') %>% 
    plot(
    title = str_glue(i18n$t("plt_title_denom_survey_comp")),
    y_label = str_glue(i18n$t("lbl_axis_y_coverage")),
    category_labels = list(
      un            = i18n$t("lbl_denom_un_proj"),
      dhis2         = i18n$t("lbl_denom_dhis2_proj"),
      anc1          = i18n$t("lbl_denom_anc1_derived"),
      penta1        = i18n$t("lbl_denom_penta1_derived"),
      penta1derived = i18n$t("opt_penta1derived"),
      anc1derived = i18n$t("opt_anc1derived")
    ),
    legend_labels = list(
      facility = i18n$t("lbl_denom_facility_based"),
      survey = i18n$t("lbl_denom_survey_national")
    )
  ) + 
  cd_report_theme()
```

**Subnational Institutional Live births**
```{r, fig.width=4.2}
cache$calculate_derived_coverage('instlivebirths', 'adminlevel_1') %>% 
  plot(
    title = str_glue(i18n$t("plt_title_cross_section_subnat"), indicator = indicator, year = year),
    x_label = str_glue(i18n$t("opt_coverage")),
    y_label = i18n$t("lbl_axis_y_region"),
    legend_labels = list(
      "un"            = i18n$t("opt_un"),
      "dhis2"         = i18n$t("opt_dhis2"),
      "anc1"          = i18n$t("opt_anc1"),
      "penta1"        = i18n$t("opt_penta1"),
      "penta1derived" = i18n$t("opt_penta1derived"),
      "anc1derived"   = i18n$t("opt_anc1derived")
    )) + 
  cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243, 4.243, 4.243), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- How well does the national projection of births align with the UN projection?
- Which denominator methods performed best at the national level for the live births coverage and penta3 coverage? And for subnational level for the two indicators?
- What denominators are selected for the maternal (instlivebirths) and vaccination (penta3) indicators in the coverage analyses? 

:::

`r run_pagebreak()`

## 2. National coverage trends: facility data and surveys

#### Antenatal care: ANC4, ANC early visit, first trimester of pregnancy

`r my_multicol_start()`

**ANC 4**
```{r, fig.width=6.3, fig.height=3}
current_indicator <- 'anc4'
indicator <- i18n$t(paste0('opt_', current_indicator))
denominator <- i18n$t(paste0("opt_", cache$get_denominator(current_indicator)))
cache$get_filtered_coverage(current_indicator, 'national') %>% 
  plot(
    title = str_glue(i18n$t('plt_title_coverage_nat_est')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = str_glue(i18n$t("plt_caption_coverage_denom")),
    labels = list(
      dhis2  = i18n$t("lbl_coverage_dhis2_est"),
      wuenic = i18n$t("lbl_coverage_wuenic_est"),
      survey = i18n$t("lbl_coverage_survey_est"),
      ci     = i18n$t("lbl_coverage_95ci")
    )) +
  cd_report_theme()
```

**ANC early visit**
```{r, fig.width=6.3, fig.height=3}
current_indicator <- 'anc_1trimester'
indicator <- i18n$t(paste0('opt_', current_indicator))
denominator <- i18n$t(paste0("opt_", cache$get_denominator(current_indicator)))
cache$get_filtered_coverage(current_indicator, 'national') %>% 
  plot(
    title = str_glue(i18n$t('plt_title_coverage_nat_est')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = str_glue(i18n$t("plt_caption_coverage_denom")),
    labels = list(
      dhis2  = i18n$t("lbl_coverage_dhis2_est"),
      wuenic = i18n$t("lbl_coverage_wuenic_est"),
      survey = i18n$t("lbl_coverage_survey_est"),
      ci     = i18n$t("lbl_coverage_95ci")
    )) +
  cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- Are the levels and trends plausible? Is there good consistency between the facility and survey data?

:::

#### Institutional Live Births

`r my_multicol_start()`

```{r, fig.width=6.3, fig.height=3}
current_indicator <- 'instlivebirths'
indicator <- i18n$t(paste0('opt_', current_indicator))
denominator <- i18n$t(paste0("opt_", cache$get_denominator(current_indicator)))
cache$get_filtered_coverage(current_indicator, 'national') %>% 
  plot(
    title = str_glue(i18n$t('plt_title_coverage_nat_est')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = str_glue(i18n$t("plt_caption_coverage_denom")),
    labels = list(
      dhis2  = i18n$t("lbl_coverage_dhis2_est"),
      wuenic = i18n$t("lbl_coverage_wuenic_est"),
      survey = i18n$t("lbl_coverage_survey_est"),
      ci     = i18n$t("lbl_coverage_95ci")
    )) +
  cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretations**

- Are the levels and trends plausible? Is there good consistency between the facility and survey data?
- How does the coverage perform compared to the targets? Is this a positive trend?

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

#### Immunization: Penta 3, Measles 1

`r my_multicol_start()`

```{r, fig.width=6.3, fig.height=3}
current_indicator <- 'penta3'
indicator <- i18n$t(paste0('opt_', current_indicator))
denominator <- i18n$t(paste0("opt_", cache$get_denominator(current_indicator)))
cache$get_filtered_coverage(current_indicator, 'national') %>% 
  plot(
    title = str_glue(i18n$t('plt_title_coverage_nat_est')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = str_glue(i18n$t("plt_caption_coverage_denom")),
    labels = list(
      dhis2  = i18n$t("lbl_coverage_dhis2_est"),
      wuenic = i18n$t("lbl_coverage_wuenic_est"),
      survey = i18n$t("lbl_coverage_survey_est"),
      ci     = i18n$t("lbl_coverage_95ci")
    )) +
  cd_report_theme()

current_indicator <- 'measles1'
indicator <- i18n$t(paste0('opt_', current_indicator))
denominator <- i18n$t(paste0("opt_", cache$get_denominator(current_indicator)))
cache$get_filtered_coverage(current_indicator, 'national') %>% 
  plot(
    title = str_glue(i18n$t('plt_title_coverage_nat_est')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = str_glue(i18n$t("plt_caption_coverage_denom")),
    labels = list(
      dhis2  = i18n$t("lbl_coverage_dhis2_est"),
      wuenic = i18n$t("lbl_coverage_wuenic_est"),
      survey = i18n$t("lbl_coverage_survey_est"),
      ci     = i18n$t("lbl_coverage_95ci")
    )) +
  cd_report_theme()

run_columnbreak()
```

::: {custom-style="Style1"}

**Interpretations**

- Are the levels and trends plausible? Is there good consistency between the facility and survey data? How do the results compare to the UN estimates (WUENIC)?
- How does the coverage perform compared to the targets? Is this a positive trend?

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

#### Percent of districts achieving high coverage targets

`r my_multicol_start()`

**ANC 4**
```{r, fig.width=4.2, fig.height=3}
current_indicator <- 'anc4'
translated_x_labels <- list(
  instlivebirths = i18n$t("opt_instlivebirths"),
  pnc48h = i18n$t("opt_pnc48h"),
  bcg = i18n$t("opt_bcg"),
  penta3 = i18n$t("opt_penta3"),
  measles1 = i18n$t("opt_measles1"),
  dropout_penta13 = i18n$t("opt_dropout_penta13"),
  dropout_penta3mcv1 = i18n$t("opt_dropout_penta3mcv1")
)

filtered_data <- cache$get_filtered_threshold(current_indicator, 'district')

admin_lvl_translated <- i18n$t(paste0("opt_", current_indicator))
rate <- i18n$t(if (current_indicator == 'opt_dropout') 'opt_rate' else 'opt_coverage')
sign <- if (current_indicator == 'opt_dropout') '<' else '≥'
group <- i18n$t(paste0("opt_", current_indicator))
coverage <- attr(filtered_data, "threshold")

# FIXED: Explicitly pass named variables into str_glue so it overrides the reactive functions in the environment
plot_title <- str_glue(
  i18n$t('plt_title_target_national'),
  admin_level = admin_lvl_translated,
  region = "",
  coverage = coverage,
  group = group,
  rate = rate,
  sign = sign
)
filtered_data %>% 
  plot(
    title = plot_title,
    y_axis = i18n$t("lbl_axis_y_pct_subnat"),
    legend_title = i18n$t("title_global_year"),
    x_labels = translated_x_labels
  ) + cd_report_theme()
```

**Child Health Indicators**

```{r, fig.width=4.2, fig.height=3}
current_indicator <- 'vaccine'
translated_x_labels <- list(
  instlivebirths = i18n$t("opt_instlivebirths"),
  pnc48h = i18n$t("opt_pnc48h"),
  bcg = i18n$t("opt_bcg"),
  penta3 = i18n$t("opt_penta3"),
  measles1 = i18n$t("opt_measles1"),
  dropout_penta13 = i18n$t("opt_dropout_penta13"),
  dropout_penta3mcv1 = i18n$t("opt_dropout_penta3mcv1")
)

filtered_data <- cache$get_filtered_threshold(current_indicator, 'district')

admin_lvl_translated <- i18n$t(paste0("opt_", current_indicator))
rate <- i18n$t(if (current_indicator == 'opt_dropout') 'opt_rate' else 'opt_coverage')
sign <- if (current_indicator == 'opt_dropout') '<' else '≥'
group <- i18n$t(paste0("opt_", current_indicator))
coverage <- attr(filtered_data, "threshold")

# FIXED: Explicitly pass named variables into str_glue so it overrides the reactive functions in the environment
plot_title <- str_glue(
  i18n$t('plt_title_target_national'),
  admin_level = admin_lvl_translated,
  region = "",
  coverage = coverage,
  group = group,
  rate = rate,
  sign = sign
)
filtered_data %>% 
  plot(
    title = plot_title,
    y_axis = i18n$t("lbl_axis_y_pct_subnat"),
    legend_title = i18n$t("title_global_year"),
    x_labels = translated_x_labels
  ) + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretations**

- Has the proportion of districts that achieved the target varied over time?

:::

`r my_multicol_stop(widths = c(4.243,4.243,4.243), space = 0.2, sep = FALSE)`

`r run_pagebreak()`

## 3. Equity

#### Equity by wealth, education, rural-urban residence (from surveys)

**InstitutionalLive Births**

`r my_multicol_start()`

```{r, fig.width=4.2}
equiplot_area(
  cache$area_survey, 
  'instlivebirths',
  title = str_glue(i18n$t("plt_title_equity_area")),
  x_title = str_glue(i18n$t("lbl_axis_y_coverage")),
  legend_title = i18n$t("lbl_leg_equity_area"),
  legend_labels = list(
    "Rural" = i18n$t("lbl_equity_area_rural"),
    "Urban" = i18n$t("lbl_equity_area_urban")
  )) +
cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_wealth(
  cache$wiq_survey, 
  'instlivebirths',
  title = str_glue(i18n$t("plt_title_equity_wealth")),
  x_title = str_glue(i18n$t("lbl_axis_y_coverage")),
  legend_title = i18n$t("lbl_leg_equity_wealth")
  ) %>%
  cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_education(
  cache$education_survey, 
  'instlivebirths',
  title = str_glue(i18n$t("plt_title_equity_education")),
  x_title = str_glue(i18n$t("lbl_axis_y_coverage")),
  legend_title = i18n$t("lbl_leg_equity_education"),
  legend_labels = list(
    "none" ~ i18n$t("lbl_equity_edu_none"),
    "primary" ~ i18n$t("lbl_equity_edu_primary"),
    "secondary+" ~ i18n$t("lbl_equity_edu_secondary")
  )) %>%
  cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243, 4.243, 4.243), space = 0.2, sep = FALSE)`

**Pentavalent 3rd Dose**

`r my_multicol_start()`

```{r, fig.width=4.2}
equiplot_area(
  cache$area_survey, 
  'penta3',
  title = str_glue(i18n$t("plt_title_equity_area")),
  x_title = str_glue(i18n$t("lbl_axis_y_coverage")),
  legend_title = i18n$t("lbl_leg_equity_area"),
  legend_labels = list(
    "Rural" = i18n$t("lbl_equity_area_rural"),
    "Urban" = i18n$t("lbl_equity_area_urban")
  )) +
cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_wealth(
  cache$wiq_survey, 
  'penta3',
  title = str_glue(i18n$t("plt_title_equity_wealth")),
  x_title = str_glue(i18n$t("lbl_axis_y_coverage")),
  legend_title = i18n$t("lbl_leg_equity_wealth")
  ) +
  cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_education(
  cache$education_survey, 
  'penta3',
  title = str_glue(i18n$t("plt_title_equity_education")),
  x_title = str_glue(i18n$t("lbl_axis_y_coverage")),
  legend_title = i18n$t("lbl_leg_equity_education"),
  legend_labels = list(
    "none" ~ i18n$t("lbl_equity_edu_none"),
    "primary" ~ i18n$t("lbl_equity_edu_primary"),
    "secondary+" ~ i18n$t("lbl_equity_edu_secondary")
  )) %>%
  cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243, 4.243, 4.243), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- Can you observe any systematic differences—such as specific groups consistently being left behind?
- Are there observable patterns of inequality (e.g., linear, concentrated at the top or bottom)? If so, what potential strategies could be implemented to reduce these inequalities?
- Are all subgroups experiencing increases or decreases in coverage/prevalence at the same pace?
- Are inequalities changing over time?

:::

#### Geographical inequalities: Health facility data 

`r my_multicol_start()`

**InstituionalLive Births**
```{r, fig.width=6.3}
current_indicator <- 'instlivebirths'
indicator <- i18n$t(paste0("opt_", current_indicator))
cache$get_filtered_inequality(indicator = current_indicator, admin_level = 'adminlevel_1') %>% 
  plot(
    title = indicator,
    subtitle = str_glue(i18n$t('lbl_inequ_subnat_admin1')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = i18n$t(paste0("plt_caption_equity_", cache$get_denominator(current_indicator))),
    legend_labels = list(
      subnational = i18n$t("lbl_inequ_coverage_subnat"),
      national = str_glue(i18n$t('title_coverage_national'))
    )
  ) + cd_report_theme()
```

**Pentavalente 3ª Dose**

```{r, fig.width=6.3}
current_indicator <- 'penta3'
indicator <- i18n$t(paste0("opt_", current_indicator))
cache$get_filtered_inequality(indicator = current_indicator, admin_level = 'adminlevel_1') %>% 
  plot(
    title = indicator,
    subtitle = str_glue(i18n$t('lbl_inequ_subnat_admin1')),
    x_axis = i18n$t("title_global_year"),
    y_axis = str_glue(i18n$t("lbl_axis_y_coverage")),
    caption = i18n$t(paste0("plt_caption_equity_", cache$get_denominator(current_indicator))),
    legend_labels = list(
      subnational = i18n$t("lbl_inequ_coverage_subnat"),
      national = str_glue(i18n$t('title_coverage_national'))
    )
  ) + cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

`r my_multicol_start()`

```{r, fig.width=3.1}
current_indicator <- 'instlivebirths'
min_year <- min(cache$data_years)
max_year <- robust_max(cache$data_years)
years <- if (is.null(cache$mapping_years)) c(min_year, max_year) else cache$mapping_years

cache$get_filtered_mapping_data(current_indicator, "adminlevel_1", 'Blues', plot_year = years) %>% 
  plot(
    title = str_glue(i18n$t("plt_title_map_dist")),
    caption = i18n$t("plt_caption_map_dhis2"),
    legend = str_glue(i18n$t("lbl_axis_y_coverage"))
  ) + cd_report_theme()
```

```{r, fig.width=3.1}
current_indicator <- 'penta3'
cache$get_filtered_mapping_data(current_indicator, "adminlevel_1", 'Blues', plot_year = years) %>% 
  plot(
    title = str_glue(i18n$t("plt_title_map_dist")),
    caption = i18n$t("plt_caption_map_dhis2"),
    legend = str_glue(i18n$t("lbl_axis_y_coverage"))
  ) + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- Como a cobertura evoluiu ao longo do tempo?
- Houve alguma mudança na desigualdade? Os pontos de dados estão se tornando mais ou menos dispersos ao longo do tempo? As estimativas de MADM (Desvio Absoluto Médio da Mediana) estão mudando ao longo do período?
- Quais regiões ou distritos são os melhores e os piores desempenhadores?

:::

`r my_multicol_stop(widths = c(3.183, 3.183, 6.365), space = 0.2, sep = FALSE)`

`r run_pagebreak()`

## 4. Mortalidade institucional

#### Tendências de Mortalidade Institucional (iMMR, iSBR)

`r my_multicol_start()`

**iMMR**
```{r, fig.width=4.2}
plot(cache$mortality_summary, indicator = 'mmr_inst') +
  cd_report_theme()
```

**iSBR**
```{r, fig.width=4.2}
plot(cache$mortality_summary, indicator = 'sbr_inst') +
  cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- O que pode ser dito sobre o nível e a tendência? Isso está alinhado com o que se espera com base nas estimativas da ONU?

:::

`r my_multicol_stop(widths = c(4.243,4.243,4.243), space = 0.2, sep = FALSE)`

#### Mortalidade Institucional por unidades admin1

`r my_multicol_start()`

```{r, fig.width=4.2}
cache$filter_mortality_summary('mmr', c(first_year, last_year)) %>% 
  plot() +  cd_report_theme()
```

```{r, fig.width=4.2}
cache$filter_mortality_summary('sbr', c(first_year, last_year)) %>% 
  plot() + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- Quais são as 3 regiões com iMMR mais altas e as regiões com iMMR e iSBR mais baixas? (nome com nível) Isso está conforme o esperado ou sugere problemas de qualidade dos dados?
- (são essas regiões mais avançadas onde se espera que a mortalidade seja menor ou há regiões menos desenvolvidas com baixa mortalidade, o que poderia indicar subnotificação significativa de óbitos)

:::

`r my_multicol_stop(widths = c(4.243,4.243,4.243), space = 0.2, sep = FALSE)`


#### Métricas de qualidade dos dados

Razão de natimortos para óbitos maternos nos dados de unidades de saúde a nível nacional

`r my_multicol_start()`

```{r, fig.width=6.3}
current_indicator <- "ratio_md_sb"
plot_mortality_plausibility(
  mortality_summary, 
  indicator = current_indicator,
  title = full_title,
  y_axis = i18n$t(paste0("ylab_", current_indicator)),
  x_axis = i18n$t("title_global_year"),
  note = i18n$t(paste0("note_", current_indicator)),
  legend_labels = list(
    median = i18n$t("lbl_median"),
    plausible = i18n$t("lbl_plausible")
  )) +
  cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- Uma razão plausível está na faixa de 5 a 25 natimortos por óbito materno. A razão nacional está dentro da faixa esperada?
- O que pode ser dito sobre as 3 regiões superiores e as 3 inferiores?
- Se a razão for superior a 25, isso pode indicar que os óbitos maternos estão mais subnotificados que os natimortos. Se for inferior a 5, os natimortos provavelmente estão subnotificados. Se a razão estiver dentro da faixa, o reporte pode ser bom se os níveis de mortalidade estiverem dentro do esperado. Caso contrário, tanto os óbitos maternos quanto os natimortos estão subnotificados.

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

Estimativa de completude da notificação de óbitos maternos e natimortos nas unidades de saúde

`r my_multicol_start()`

```{r, fig.width=6.3}
cache$summarise_completeness_ratio('mmr') %>%
  plot() +
  cd_report_theme()
```

```{r, fig.width=6.3}
cache$summarise_completeness_ratio('sbr') %>%
  plot() +
  cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretações**

- Comente sobre a completude da notificação de MMR e SBR institucionais com base no MMR populacional e na razão Comunidade para Institucional

:::

`r run_pagebreak()`

## 5. Utilização de serviços de saúde curativos para crianças doentes

#### Utilização de serviços ambulatoriais e hospitalares 

`r my_multicol_start()`

```{r, fig.width=6.3}
cache$filter_service_utilization('national', 'opd') %>% 
  plot() + cd_report_theme()
```

```{r, fig.width=6.3}
cache$filter_service_utilization('national', 'ipd') %>% 
  plot() + cd_report_theme()

run_columnbreak()
```

::: {custom-style="Style1"}

**Interpretações**

- Qual é o número de visitas ambulatoriais (OPD) por criança por ano em 2024 e a tendência ao longo do tempo? É inferior a 1 visita por ano, o que sugeriria baixo acesso?
- O que pode ser dito sobre a qualidade dos dados das visitas OPD e IPD? Há consistência nos números reportados entre os anos?
- Qual é o número de visitas hospitalares (IPD) por 100 crianças por ano entre 2019-2024, está aumentando? É inferior a 2 por 100 crianças menores de cinco anos, o que sugeriria baixo acesso?
- O que pode ser dito sobre as visitas OPD e admissões por região/província em 2024? Qual a magnitude da diferença entre as regiões superiores e inferiores?

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

#### Utilização de serviços regionais/provinciais

`r my_multicol_start()`

```{r, fig.width=4.2}
cache$filter_service_utilization('national', 'opd') %>% 
  plot() + cd_report_theme()
```

```{r, fig.width=4.2}
cache$filter_service_utilization('national', 'ipd') %>% 
  plot() + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- Quais são as 3 regiões com as maiores taxas de OPD e IPD e as 3 regiões com as menores (nome da região com valores)? Alguma razão? Possíveis problemas de dados?

:::

`r my_multicol_stop(widths = c(4.243,4.243,4.243), space = 0.2, sep = FALSE)`

`r my_multicol_start()`

#### Índice Preventivo vs Curativo de MCH

```{r, fig.width=6.3}
cache$generate_admin1_mch_curative_index() %>% 
  plot(
    labels = list(
      title          = i18n$t("lbl_mch_curative_title"),
      x_axis         = i18n$t("lbl_mch_prev_index_x"),
      y_axis         = i18n$t("lbl_curative_index_y"),
      q_top_left     = i18n$t("lbl_quad_low_prev_high_cur"),
      q_top_right    = i18n$t("lbl_quad_high_prev_high_cur"),
      q_bottom_left  = i18n$t("lbl_quad_low_prev_low_cur"),
      q_bottom_right = i18n$t("lbl_quad_high_prev_low_cur")
    )
  ) + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- Qual é a taxa de letalidade entre admissões de menores de cinco anos? Quais são as tendências?
- O que isso indica sobre a qualidade do atendimento?

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

`r run_pagebreak()`

## 6. Progresso e desempenho do sistema de saúde

#### Insumos do sistema de saúde

`r my_multicol_start()`

```{r, fig.width=6.3, fig.height = 3.5}
latest_year <- max(cache$data_years)

cache$generate_health_system_table(
  labels = list(
    section = list(
      infrastructure = i18n$t("sec_infrastructure"),
      workforce      = i18n$t("sec_workforce"),
      private_sector = i18n$t("sec_private_sector")
    ),
    indicator = list(
      fac_density   = i18n$t("ind_fac_density"),
      hosp_share    = i18n$t("ind_hosp_share"),
      hosp_density  = i18n$t("ind_hosp_density"),
      bed_density   = i18n$t("ind_bed_density"),
      hwf_density   = i18n$t("ind_hwf_density"),
      skill_mix     = i18n$t("ind_skill_mix"),
      private_share = i18n$t("ind_private_share"),
      ngo_share     = i18n$t("ind_ngo_share")
    ),
    unit = list(
      per_10k  = i18n$t("unit_per_10k"),
      per_100k = i18n$t("unit_per_100k"),
      pct      = "%"
    )
  )) %>%
  plot(
    year = latest_year, 
    indicator_label = i18n$t("title_global_indicator"),
    value_label     = i18n$t("lbl_value"),
    unit_label      = i18n$t("lbl_unit")
  ) %>% 
  padding(padding = 1.5, part = 'all')
```

::: {custom-style="Style1"}

**Interpretações**

- Observação sobre a completude dos dados (incluindo o setor privado)? 
- O que pode ser dito sobre os insumos do sistema de saúde nacional? Como eles se comparam aos referenciais?
Densidade de Unidades de Saúde (Referencial: 2)
Densidade de leitos (Referencial: 25)
Densidade de força de trabalho em saúde (Referencial: 23 – necessária para avançar significativamente na redução da mortalidade materna e infantil com alta taxa de partos assistidos por profissionais qualificados (OMS).
44,5 por 10.000 habitantes para alcançar cobertura universal de saúde

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

#### Insumos do sistema de saúde por região/província

`r my_multicol_start()`

```{r, fig.width=4.2}
nat_metrics <- cache$health_system_metrics_national
current_indicator <- "ratio_fac_pop"
cache$health_system_metrics_admin1 %>%
  plot(
    indicator = current_indicator,
    national_value = nat_metrics[[current_indicator]],
    title         = i18n$t(paste0('title_metric_', current_indicator)),
    x_axis        = i18n$t(paste0('xlab_metric_', current_indicator)),
    legend_labels = list(
      "FALSE" = i18n$t("lbl_below_benchmark"),
      "TRUE"  = i18n$t("lbl_meets_benchmark"),
      "threshold_line" = i18n$t("lbl_target_benchmark"), 
      "national_line"  = i18n$t("lbl_national_average")
    )
  ) +
  cd_report_theme()
```

```{r, fig.width=4.2}
current_indicator <- "ratio_hos_pop"
cache$health_system_metrics_admin1 %>%
  plot(
    indicator = current_indicator,
    national_value = nat_metrics[[current_indicator]],
    title         = i18n$t(paste0('title_metric_', current_indicator)),
    x_axis        = i18n$t(paste0('xlab_metric_', current_indicator)),
    legend_labels = list(
      "FALSE" = i18n$t("lbl_below_benchmark"),
      "TRUE"  = i18n$t("lbl_meets_benchmark"),
      "threshold_line" = i18n$t("lbl_target_benchmark"), 
      "national_line"  = i18n$t("lbl_national_average")
    )
  ) +
  cd_report_theme()
```

```{r, fig.width=4.2}
current_indicator <- "ratio_hstaff_pop"
cache$health_system_metrics_admin1 %>%
  plot(
    indicator = current_indicator,
    national_value = nat_metrics[[current_indicator]],
    title         = i18n$t(paste0('title_metric_', current_indicator)),
    x_axis        = i18n$t(paste0('xlab_metric_', current_indicator)),
    legend_labels = list(
      "FALSE" = i18n$t("lbl_below_benchmark"),
      "TRUE"  = i18n$t("lbl_meets_benchmark"),
      "threshold_line" = i18n$t("lbl_target_benchmark"), 
      "national_line"  = i18n$t("lbl_national_average")
    )
  ) +
  cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243,4.243,4.243), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

---

- Como varia o número de unidades de saúde por unidades admin1?
- Como varia a densidade hospitalar por unidades admin1?
- Como varia a densidade da força de trabalho em saúde por unidades admin1?
- Quais são as unidades admin1 superiores e inferiores? Elas são consistentes em todos os indicadores?

---

:::

#### Resultados do sistema de saúde por insumos a nível subnacional

`r my_multicol_start()`

```{r, fig.width=6.3}
current_indicator <- "ratio_fac_pop"
cache$generate_phc_scatter_data(indicator = current_indicator) %>%
  plot(
    title  = i18n$t(paste0("title_scatter_", current_indicator)),
    x_axis = i18n$t(paste0("xlab_", current_indicator)),
    y_axis = i18n$t("ylab_phc_scatter"),
    quad_labels = list(
      high_high = i18n$t(paste0("lbl_hh_", current_indicator)),
      low_high  = i18n$t(paste0("lbl_lh_", current_indicator)),
      high_low  = i18n$t(paste0("lbl_hl_", current_indicator)),
      low_low   = i18n$t(paste0("lbl_ll_", current_indicator))
    )
  ) + 
  cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- A interpretação deve focar em se a imagem obtida tem validade. Isso pode ser afirmado se confirmar algumas expectativas, como regiões mais desenvolvidas apresentarem melhores resultados.
- Descreva as regiões/províncias com desempenho ruim e bom

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

#### Serviços do setor privado e RMNCAH

`r my_multicol_start()`

```{r, fig.width=4.2}
cache$national_private_share %>% 
  plot() + cd_report_theme()
```

```{r, fig.width=4.2}
cache$area_private_share %>% 
  plot() + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretações**

- Quais indicadores têm maior participação do setor privado?
- Existem diferenças entre áreas rurais e urbanas?

:::

`r my_multicol_stop(widths = c(4.243,4.243,4.243), space = 0.2, sep = FALSE)`
