---
title: "`r params$country`"
output: 
  officedown::rdocx_document:
    reference_docx: synthesis-template.docx
params:
  cache: NULL
  i18n: NULL
  adminlevel_1: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  # fig.width=7, 
  # fig.height=5, 
  dpi=300
)

library(officedown)
library(officer)
library(cd2030.core)
library(dplyr)
library(purrr)
library(reactable)

cache <- params$cache
data <- cache$countdown_data
country <- cache$country
data_years <- cache$data_years
years_range <- paste0(min(data_years, na.rm = TRUE), '-', max(data_years, na.rm = TRUE))

layout <- cd_multicol_factory(width = 13.93, height = 22.0, orient = "portrait", margins = c(0.5, 0.5, 0.5, 0.5))

my_multicol_start <- layout$start
my_multicol_stop <- layout$stop
```

### Analysis of vaccine health indicators for `r years_range`: Synthesis chartbook 
### Countdown to 2030 in partnership with `r country` Ministry of Health, Global Financing Facility, WHO, WAHO, UNICEF

> Country analytical team names and affiliation

# KEY FINDINGS

## 1. Health facility data quality assessment: numerators and denominators

**NUMERATORS:** Routinely reported health facility data are an important data source for health indicators. The data are reported by health facilities on events such as immunizations given, or live births attended. As with any data, quality is an issue. Data are assessed for completeness of reporting by health facilities, extreme outliers and internal consistency. Appropriate adjustments are made to the data before use to compute statistics.

#### Summary of reported health facility data quality, DHIS2, `r years_range`

`r my_multicol_start()`

```{r, fig.width=8}
overall_score <- if (is.null(adminlevel_1)) {
  cache$calculate_overall_score("national")
} else {
  cache$calculate_overall_score("adminlevel_1", region())
}

overall_score %>% plot(cache$data_years, width = 8)
```

`r run_columnbreak()`

::: {custom-style="Style1"}

**Interpretations**

- What is the overall quality of the data as assessed by the overall annual data quality score?
- Is there a data quality pattern by year for which there is an explanation? 
- Are there certain regions or other subnational units that are particularly problematic?
- Are there certain reporting forms or services (e.g., antenatal care, labour and delivery, immunization) that are problematic? Was an adjustment done for incomplete reporting (provide the k value)?
- Is there good consistency between reported numbers of ANC1 and penta1? If not, what could be the explanation?

:::

`r my_multicol_stop(widths = c(8, 4), space = 0.2, sep = TRUE)`

`r my_multicol_start()`

Numerator: facility data quality  - example 1
Explain the observation on data quality (one bullet)

```{r, fig.width=6.3, fig.height=3.5}
plot_comparison_anc1_penta1(data) +
  cd_report_theme()

```
Numerator: facility data quality  - example 2
Explain the observation on data quality (one bullet)

```{r , fig.width=6.3, fig.height=3.5}
cache$calculate_district_reporting_rate(adminlevel_1) %>% 
  plot() + cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`


**DENOMINATORS:** Service coverage is defined as the population who received the service (numerator) divided by the population who need the services: (the denominator). We test four options for denominator measures using institutional live births and Pent-3 immunization coverage (Figures 2c and 2d). The quality of the population projections in DHIS2 is assessed through consistency over time and comparison with the UN projections. Two denominators are also derived using near universal service such as ANC-1 and Penta-1. The most plausible is identified for use to generate other statistics.

`r my_multicol_start()`

**Total Livebirths**
```{r, fig.width=4.2}
cache$denominator_metrics %>% 
  plot(metric = "births") + cd_report_theme()
```
**Institutional Deliveries**
```{r, fig.width=4.2}
cache$calculate_derived_coverage('ideliv', 'national') %>% 
  plot() + cd_report_theme()
```
**Penta 3**
```{r, fig.width=4.2}
cache$calculate_derived_coverage('penta3', 'national') %>% 
  plot() + cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243, 4.243, 4.243), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- How well does the national projection of births align with the UN projection?
- Which denominator methods performed best at the national level for the live births coverage and penta3 coverage? And for subnational level for the two indicators?
- What denominators are selected for the maternal (ideliv) and vaccination (penta3) indicators in the coverage analyses? 

:::

`r run_pagebreak()`

## 2. National coverage trends: facility data and surveys

#### ANC1, Institutional deliveries

`r my_multicol_start()`

**ANC 1**
```{r, fig.width=6.3, fig.height=3}
cache$get_filtered_coverage('anc1', 'national') %>%
  plot() + cd_report_theme()
```

**Penta 1**
```{r, fig.width=6.3, fig.height=3}
cache$get_filtered_coverage('ideliv', 'national') %>%
  plot() + cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- Are the levels and trends plausible? Is there good consistency between the facility and survey data?

:::

#### Measles1

`r my_multicol_start()`

```{r, fig.width=6.3, fig.height=3}
cache$get_filtered_coverage('penta3', 'national') %>%
  plot() + cd_report_theme()
  
cache$get_filtered_coverage('measles1', 'national') %>%
  plot() + cd_report_theme()
  
run_columnbreak()
```

::: {custom-style="Style1"}

**Interpretations**

- Are the levels and trends plausible? Is there good consistency between the facility and survey data?
- How does the coverage perform compared to the targets? Is this a positive trend?

:::

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

#### Percent of districts achieving high coverage targets

`r my_multicol_start()`

**Vaccine**
```{r, fig.width=6.365, fig.height=3}
cache$get_filtered_threshold('vaccine', 'district') %>% 
   plot() + cd_report_theme()
```

**Dropout**
```{r, fig.width=6.365, fig.height=3}
cache$get_filtered_threshold('dropout', 'district') %>% 
   plot() + cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- Has the proportion of districts that achieved the target varied over time?

:::


`r run_pagebreak()`

## 3. Equity

#### Equity by wealth, education, rural-urban residence (from surveys)

**Institutional Livebirths**

`r my_multicol_start()`

```{r, fig.width=4.2}
equiplot_area(cache$area_survey, 'instlivebirths') +
  cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_wealth(cache$wiq_survey, 'instlivebirths') +
  cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_education(cache$education_survey, 'instlivebirths') +
  cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243, 4.243, 4.243), space = 0.2, sep = FALSE)`

**Pentavalent 3rd Dose**

`r my_multicol_start()`

```{r, fig.width=4.2}
equiplot_area(cache$area_survey, 'penta3') +
  cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_wealth(cache$wiq_survey, 'penta3') +
  cd_report_theme()
```

```{r, fig.width=4.2}
equiplot_education(cache$education_survey, 'penta3') +
  cd_report_theme()
```

`r my_multicol_stop(widths = c(4.243, 4.243, 4.243), space = 0.2, sep = FALSE)`

::: {custom-style="Style1"}

**Interpretations**

- Can you observe any systematic differences—such as specific groups consistently being left behind?
- Are there observable patterns of inequality (e.g., linear, concentrated at the top or bottom)? If so, what potential strategies could be implemented to reduce these inequalities?
- Are all subgroups experiencing increases or decreases in coverage/prevalence at the same pace?
- Are inequalities changing over time?

:::

#### Geographical inequalities: Health facility data 

`r my_multicol_start()`

**Instituional Deliveries**
```{r, fig.width=6.3}
cache$get_filtered_inequality('ideliv', 'adminlevel_1') %>% 
  plot() + cd_report_theme()
```

**Pentavalent 3rd Dose**

```{r, fig.width=6.3}
cache$get_filtered_inequality('penta3', 'adminlevel_1') %>% 
  plot() + cd_report_theme()
```

`r my_multicol_stop(widths = c(6.365, 6.365), space = 0.2, sep = FALSE)`

`r my_multicol_start()`

```{r, fig.width=3.1}
cache$get_filtered_mapping_data('ideliv', 'adminlevel_1', 'Greens') %>% 
  plot() + cd_report_theme()
```

```{r, fig.width=3.1}
cache$get_filtered_mapping_data('ideliv', 'adminlevel_1', 'Blues') %>% 
  plot() + cd_report_theme()
```

::: {custom-style="Style1"}

**Interpretations**

- How has coverage evolved over time?
- Has there been any change in inequality? Are the data points becoming more or less dispersed over time? Are the MADM (Mean Absolute Deviation from the Median) estimates changing throughout the period?
- Which regions or districts are the best and worst performers?

:::

`r my_multicol_stop(widths = c(3.183, 3.183, 6.365), space = 0.2, sep = FALSE)`
